Generation of TypeScript Declaration Files from JavaScript Code

### 2021-08-16 mplr-2021/main.tex
Remove typo pointed out in the feedback
Add copyright and future work

\usepackage{microtype}

@@

@@

\author{Peter Thiemann}
\affiliation{%
  \institution{Albert-Ludwigs-Universit{\"a}t Freiburg}
  \city{Freiburg}
  \country{Germany}
}
\email{thiemann@informatik.uni-freiburg.de}

@@

We aim to improve on this situation by providing a tool that generates
TypeScript declaration files automatically. To do so, we rely on we rely on run-time information
gathered from the examples provided
by the developer as part of the documentation of a library. If these
examples are sufficiently rich, then our toolchain can generate
high-quality declaration files for the library. This way we take
advantage of 
best practices in the dynamic languages community which favors
examples and tests over writing out type signatures.

@@

The TypeScript project provides a guide on how to write high-quality declaration
files\footnote{https://www.typescriptlang.org/docs/handbook/declaration-files/by-example.html}. The guide
explains the main concepts through examples. We selected one example for each template
from the guide and
used \texttt{dts-generate} to generate a corresponding declaration file, as shown in
\figref{fig:typescript-templates-by-example}.

@@

>>>>

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{microtype}

@@

\copyrightyear{2021}
\acmYear{2021}
\setcopyright{acmlicensed}\acmConference[MPLR '21]{Proceedings of the 18th ACM SIGPLAN International Conference on Managed Programming Languages and Runtimes}{September 29--30, 2021}{Münster, Germany}
\acmBooktitle{Proceedings of the 18th ACM SIGPLAN International Conference on Managed Programming Languages and Runtimes (MPLR '21), September 29--30, 2021, Münster, Germany}
\acmPrice{15.00}
\acmDOI{10.1145/3475738.3480941}
\acmISBN{978-1-4503-8675-3/21/09}

@@

\author{Peter Thiemann}
\affiliation{%
  \institution{Albert-Ludwigs-Universität Freiburg}
  \city{Freiburg}
  \country{Germany}
}
\email{thiemann@informatik.uni-freiburg.de}

@@

We aim to improve on this situation by providing a tool that generates
TypeScript declaration files automatically. To do so, we rely on run-time information
gathered from the examples provided
by the developer as part of the documentation of a library. If these
examples are sufficiently rich, then our toolchain can generate
high-quality declaration files for the library. This way we take
advantage of 
best practices in the dynamic languages community which favors
examples and tests over writing out type signatures.

@@

The TypeScript project provides a guide on how to write high-quality declaration
files\footnote{\url{https://www.typescriptlang.org/docs/handbook/declaration-files/by-example.html}}. The guide
explains the main concepts through examples. We selected one example for each template
from the guide and
used \texttt{dts-generate} to generate a corresponding declaration file, as shown in
\figref{fig:typescript-templates-by-example}.

@@

Return types could be defined more accurately by analyzing the interactions tracked on
them. We consider that enhancing the run-time information by executing tests already
present in the codebase is an approach worth following as future work.
